DOpElib:\\ Differential Equations and Optimization Environment

### 2013-12-14 Examples/Documentation/introduction.tex
Kleine Aenderungen, siehe Mail
Update Doku in Einklang mit Christians und Winnis Bemerkungen/Zustimmung
Bemerkung 3.0.1 zu fullmem und store_on_disc

\section{Developers}
\label{sec:contrib}
The library is currently maintained by 
\begin{itemize}
  \item Christian Goll (Heidelberg University)
  \item Thomas Wick (The University of Texas at Austin)
  \item Winnifried Wollner (University of Hamburg)
\end{itemize}

@@

\subsubsection{Vectors}
\begin{itemize}
\item \texttt{include/statevector.h} This stores all dofs in space and time for the state 
  variable $u$. It is possible to select whether all this should be kept in memory or 
  or unused parts can be written to the hard disk.
\item \texttt{include/controlvector.h} This stores all dofs in space and time for the 
  control variable $q$. At present no time dependence is implemented.
\item \texttt{include/constraintvector.h} This stores all dofs in space and time for the 
  non PDE constraints (and corresponding multipliers). 
  At present no time dependence is implemented.
\end{itemize}

>>>>

\section{Contributors \& Developers}
\label{sec:contrib}
The library is currently maintained by 
\begin{itemize}
  \item Christian Goll (Heidelberg University)
  \item Thomas Wick (The University of Texas at Austin)
  \item Winnifried Wollner (University of Hamburg)
\end{itemize}

@@

\subsubsection{Vectors}
\begin{itemize}
\item \texttt{include/statevector.h} This stores all dofs in space and time for the state 
  variable $u$. It is possible to select whether all this should be kept in memory or 
  or unused parts can be written to the hard disk.
\item \texttt{include/controlvector.h} This stores all dofs in space and time for the 
  control variable $q$. At present no time dependence is implemented.
\item \texttt{include/constraintvector.h} This stores all dofs in space and time for the 
  non PDE constraints (and corresponding multipliers). 
  At present no time dependence is implemented.
\end{itemize}
\begin{remark}
\label{remark_state_behavior}
We notice that the behavior of the statevector can be chosen as 
\texttt{fullmem} or \texttt{store\underline{ }on\underline{ }disc}. In the
first state, the RAM memory of the computer is used. In the second state,
all vectors are written on disc, to avoid the RAM. This might take some 
time at the beginning of a new executing program (cleary depending 
on the number of spatial and temporal unknowns and the capabilities of your 
local machine). In addition, if the program aborts abnormally in the 
using \texttt{store\underline{ }on\underline{ }disc} behavior, please make 
sure to remove manually the \texttt{tmp\underline{ }state} folder in your 
\texttt{Results} folder. 
\end{remark}

### 2013-12-14 Examples/PDE/InstatPDE/Example2/content.tex
Bemerkung 3.0.1 zu fullmem und store_on_disc

>>>>

In addition, we notice that specifically the FSI 3 version of this 
code introduces a large amount of total DOFs. Probably, your machine 
will terminate in \texttt{fullmem} modus. Here you might change the 
statevector behavior to \texttt{store\underline{ }on\underline{ }disc}.
However, it takes some time to write all vectors locally on your disc.
On a Lenovo X230, it takes $3$ minutes. In a future version of the library,
we plan to introduce a less expensive statevector behavior.
We also refer to Remark \ref{remark_state_behavior}.
